### 2014-12-12 paper.tex
updated bibliography
More analysis, and tables of regression coefs in the paper

\usepackage{fancyhdr,hyperref,setspace,booktabs,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage[margin=1in,includehead]{geometry}

@@

  A given plan has symmetry if "similary-situated parties are treated equally", thus expecting that an even split in votes across two parties would have an even split in seats. Furthermore, if a plaintiff challenging a redistricting plan can demonstrate partisan intent and asymmetry, it would be sufficient for the burden of proof to shift to the state.  Nevertheless, while acknowledging the viability of symmetry as a metric to determine a discriminatory impact on voters, the court failed to establish an accepted standard or test to determine illegal gerrymandering.  Existing measures at the time, as calculated by social scientists, used hypothetical models to predict how election outcomes would turn out, given certain shifts in the electorate and certain vote shares in a given election. The court rejected the notion of using hypothetical models for a standard of constitutionality. \cite{LULAC v. Perry, 2006} \\

@@

\subsection{Redistricting Processes}
Another key aspect when discussing gerrymandering is the political processes involved in redistricting.  The Constitution provides states with the ability to create their own rules in how districts are drawn, with the provisions that states will ensure balanced district populations, and that districts are redrawn at least every 10 years \cite{LULAC v. Perry, 2006}.\\

@@

>>>>

\usepackage{fancyhdr,hyperref,setspace,booktabs,amsmath,multirow,mathpazo}
\usepackage[pdftex]{graphicx}
\usepackage[margin=1in,includehead]{geometry}

@@

  A given plan has symmetry if "similary-situated parties are treated equally", thus expecting that an even split in votes across two parties would have an even split in seats. Furthermore, if a plaintiff challenging a redistricting plan can demonstrate partisan intent and asymmetry, it would be sufficient for the burden of proof to shift to the state.  Nevertheless, while acknowledging the viability of symmetry as a metric to determine a discriminatory impact on voters, the court failed to establish an accepted standard or test to determine illegal gerrymandering.  Existing measures at the time, as calculated by social scientists, used hypothetical models to predict how election outcomes would turn out, given certain shifts in the electorate and certain vote shares in a given election. The court rejected the notion of using hypothetical models for a standard of constitutionality. \cite{LULAC v. Perry} \\

@@

\subsection{Redistricting Processes}
Another key aspect when discussing gerrymandering is the political processes involved in redistricting.  The Constitution provides states with the ability to create their own rules in how districts are drawn, with the provisions that states will ensure balanced district populations, and that districts are redrawn at least every 10 years \cite{LULAC v. Perry}.\\

@@

  \subsection{Compactness and Efficiency Gap}

  \begin{table}
    \begin{center}
      \begin{tabular}{lrrrr}\toprule
        \multirow{2}{*}{Metric} & \multicolumn{2}{c}{Efficiency gap (seats)} & \multicolumn{2}{c}{Efficiency gap (\%)} \\
               & \multicolumn{1}{c}{Seat share} & \multicolumn{1}{c}{Wasted votes} & \multicolumn{1}{c}{Seat share} & \multicolumn{1}{c}{Wasted votes} \\\midrule
        \multirow{2}{*}{Area vs.~Perimeter} & -3.24 & -3.26 & -18.1 & -6.6 \\
        & (1.81) & (2.04) & (14.4) & (14.7) \\\midrule
        \multirow{2}{*}{Convex Hull Area} & -3.80 & -3.73 & -13.4 & 1.0 \\
        & (2.00) & (2.26) & (16.2) & (16.4) \\\midrule
        \multirow{2}{*}{Convex Hull Population} & -2.45 & -2.24 & -16.4 & -10.4 \\
        & (1.76) & (1.99) & (13.8) & (14.0) \\\midrule
        \multirow{2}{*}{Moment of Area} & -5.67* & -5.63 & -19.1 & -6.8 \\
        & (2.52) & (2.85) & (20.6) & (21.0) \\\midrule
        \multirow{2}{*}{Moment of Population} & -0.69* & -0.71* & -3.3 & -1.6 \\
        & (0.29) & (0.33) & (2.4) & (2.4) \\\bottomrule
      \end{tabular}
      \caption{Regression coefficients for efficiency gap regressed over each compactness metric separately on all states with at least three districts.  * denotes $p<.05$ (two-tailed test); standard errors in parentheses.\label{t:efficiency3}}
    \end{center}
  \end{table}

  \begin{table}
    \begin{center}
      \begin{tabular}{lrrrr}\toprule
        Metric & \multicolumn{2}{c}{Efficiency gap (seats)} & \multicolumn{2}{c}{Efficiency gap (\%)} \\
               & \multicolumn{1}{c}{Seat share} & \multicolumn{1}{c}{Wasted votes} & \multicolumn{1}{c}{Seat share} & \multicolumn{1}{c}{Wasted votes} \\\midrule
        \multirow{2}{*}{Area vs.~Perimeter} & -7.92 & -9.91 & -76.2* & -84.3* \\
        & (5.10) & (6.03) & (34.4) & (36.4) \\\midrule
        \multirow{2}{*}{Convex Hull Area} & -13.50* & -16.12* & -114.2* & -126.2* \\
        & (5.77) & (6.90) & (38.8) & (40.7) \\\midrule
        \multirow{2}{*}{Convex Hull Population} & -9.49* & -9.75 & -72.0* & -70.6 \\
        & (4.24) & (5.36) & (30.7) & (34.3) \\\midrule
        \multirow{2}{*}{Moment of Area} & -15.99** & -16.55* & -125.8** & -128.9** \\
        & (4.22) & (5.81) & (27.8) & (32.3) \\\midrule
        \multirow{2}{*}{Moment of Population} & -2.91 & -3.31 & -26.0* & -26.8* \\
        & (1.38) & (1.68) & (9.1) & (10.1) \\\bottomrule
      \end{tabular}
      \caption{Regression coefficients for efficiency gap regressed over each compactness metric separately on all states with at least ten districts.  * denotes $p<.05$, ** denotes $p<.01$ (two-tailed test); standard errors in parentheses.\label{t:efficiency10}}
    \end{center}
  \end{table}
